\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2011-01-30 doc/USER_MANUAL/manual_SPECFEM3D.tex
generated new small versions of the covers for the Web site, and removed old comments from the list of authors.

\section*{Authors}
The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe (IPGP) in Paris, France from 1994 to 1997.\\

Since then it has been developed and maintained by a development team: in alphabetical order,
Piero Basini,
C\'eline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Min Chen,
Hom Nath Gharti,
Vala Hj\"orleifsd\'ottir,
%%%%Emiljana Jorgji,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Dennis McRitchie,
Matthias Meschede,
David Mich\'ea,
Tarje Nissen-Meyer,
Daniel Peter,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Hejun Zhu.\\
%\toall{add full list of developers here and update the AUTHORS file accordingly}

>>>>

\section*{Authors}
The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe (IPGP) in Paris, France from 1995 to 1997.\\

Since then it has been developed and maintained by a development team: in alphabetical order,
Piero Basini,
C\'eline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Min Chen,
Hom Nath Gharti,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Dennis McRitchie,
Matthias Meschede,
David Mich\'ea,
Tarje Nissen-Meyer,
Daniel Peter,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Hejun Zhu.\\
%\toall{add full list of developers here and update the AUTHORS file accordingly}
